Imputation

### 2017-07-22 imputation.Rmd
error? need rerun

ggsave("hist-NA.png", width = 1300, height = 900, scale = 1/75)
```

@@

@@

ggsave("error-impute.png", width = 1000, height = 1000, scale = 1/75)
```

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = "backingfiles/tmp.bed",
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 / 14.0 hours
```

>>>>

ggsave("figures/hist-NA.png", width = 1300, height = 900, scale = 1/75)
```

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = bedfile,
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 / 14.0 hours
```

@@

ggsave("figures/error-impute.png", width = 1000, height = 1000, scale = 1/75)
```
